\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-06-09 forwards-and-backwards.tex
Update on Overleaf.

Potential reproduction events occur at times $\tau_a + s$
for each point $(s, v, y, \kappa) \in \Pi_a$.
We say `potential' since if the resulting level is greater than $N$,
the event does not happen.
If this is the $j^\text{th}$ point in $\Pi_a$,
the new label is $a \concat j$, the (potential) birth time is $\tau_{a \concat j} = \tau_a + s$.
For convenience define
$$
    \ell(x, y, \eta, v)
    =
    \frac{
        v
    }{
        2 N^{-1} \theta \gamma(x, \eta) r(x + y, \eta)
    } ,
$$
and using this, the (potential) new level is
\begin{equation*}
    U_{a \concat j}(\tau_{a \concat j})
    =
    U_a(\tau_{a \concat j})
    +
    \ell(X_a(\tau_{a \concat j}-), y, \eta(\tau_{a \concat j}-), v) .
\end{equation*}
If $U_{a \concat j}(\tau_{a \concat j}) < N$,
the new individual labeled $a \concat j$ is produced,
and $\kappa$ determines which label is associated with the new location,
so
\begin{align*}
    X_{a \concat j}(\tau_{a \concat j})
    &=
    X_a(\tau_{a \concat j}-) + (1 - \kappa) y .
\end{align*}
On the other hand
if $U_{a \concat j}(\tau_{a \concat j}) \ge N$, then $X_a$ is unchanged and $X_{a \concat j}$ is undefined,
so
\begin{align} \label{eqn:X_line_of_descent}
    X_a(\tau_{a \concat j})
    &=
    X_a(\tau_{a \concat j}-) + \kappa y \ind_{U_{a \concat j}(\tau_{a \concat j}) < N} .
\end{align}
Recall that the parental \emph{individual} always retains their spatial location,
so that $\kappa = 0$ corresponds to the parent being assigned a new level,
and our line of descent switching to the offspring.

@@

@@

\bibliographystyle{plainnat}
\bibliography{refs.bib}

>>>>

Potential reproduction events occur at times $\tau_a + s$
for each point $(s, v, y, \kappa) \in \Pi_a$.
We say `potential' since if the resulting level is greater than $N$,
the event does not happen.
If this is the $j^\text{th}$ point in $\Pi_a$,
the new label is $a \concat j$, the (potential) birth time is $\tau_{a \concat j} = \tau_a + s$.
For convenience define
$$
    \ell(x, y, \eta, v)
    =
    \frac{
        v
    }{
        2 N^{-1} \theta \gamma(x, \eta) r(x + y, \eta)
    } ,
$$
and using this, the (potential) new level is
\begin{equation*}
    U_{a \concat j}(\tau_{a \concat j})
    =
    U_a(\tau_{a \concat j})
    +
    \ell(X_a(\tau_{a \concat j}-), y, \eta(\tau_{a \concat j}-), v) .
\end{equation*}
If $U_{a \concat j}(\tau_{a \concat j}) < N$,
the new individual labeled $a \concat j$ is produced,
\plr{TODO: explain why this does the right thing}
and $\kappa$ determines which label is associated with the new location,
so
\begin{align*}
    X_{a \concat j}(\tau_{a \concat j})
    &=
    X_a(\tau_{a \concat j}-) + (1 - \kappa) y .
\end{align*}
On the other hand
if $U_{a \concat j}(\tau_{a \concat j}) \ge N$, then $X_a$ is unchanged and $X_{a \concat j}$ is undefined,
so
\begin{align} \label{eqn:X_line_of_descent}
    X_a(\tau_{a \concat j})
    &=
    X_a(\tau_{a \concat j}-) + \kappa y \ind_{U_{a \concat j}(\tau_{a \concat j}) < N} .
\end{align}
Recall that the parental \emph{individual} always retains their spatial location,
so that $\kappa = 0$ corresponds to the parent being assigned a new level,
and our line of descent switching to the offspring.

@@

In this section,
we will prove tightness
of the spatial and level trajectory
of a line of descent
(constructed in \S \ref{sec: individual lines of descent})
as a forward-in-time process.

In Appendix \ref{sec: Topologies on Lookdown},
we will prove that
tightness of the whole lookdown process
holds given
tightness of 
all ancestral lineages
in a countable product topology.

To prove tightness of the 
spatial and level locations
of a typical line of descent,
we will show that the
jumps in
spatial and level locations
of the line of descent
in finite time
can be controlled.

Recall that the lines of descents
track chains of descendant
individuals forwards through time following the \textit{levels}.

\subsubsection{Tightness of Spatial Trajectories}
Before proving tightness of our spatial trajectories, 
note that for a fixed label
$a=(a_0,a_1,..,a_k)$,
the spatial evolution of 
$X^N_{a}(t)$ for $t \geq \tau^N_{a}$
is determined
purely by the last term 
in Equation \eqref{eq: space_across_lineage}.

As a result, the spatial jumps are 
driven by 
an underlying Poisson point process. 
It is therefore sufficient
to prove that square of 
these increments are bounded
in small time scales.

\begin{lemma} \label{lem: tightness of individual spatial trajectory}
For fixed $a=(a_0,a_1,..,a_k)$,
$\{(X^{N}_{a}(t))_{t \geq \tau^{N}_a}: N \in \mathbb{N},  \}$ is relatively compact in 
$D_{\mathbb{R}^d}[0,\infty )$ where $\mathbb{R}^d$ is equipped with the standard Euclidean metric. 
\end{lemma}
\begin{proof}
We write $S_{t,r}:=(t,t+r  ]\times [0,\infty )\times [0,1]\times 
\{0,1\}$ to be the region for the Poisson measure driving $(X^{N}_{a}(t))_{t \geq \tau_a}$ between time $t$ and $(t+r)$ and write $\tilde\Pi_{\tau_u}(ds,dv,dy,d\kappa):=\Pi_{\tau_u}(ds,dv,dy, d\kappa) - ds\times dv\times dy \times (\frac{1}{2}\delta_{0}+\frac{1}{2}\delta_{1})d\kappa$ to be the compensated Poisson point process of $\Pi_{\tau_u}$. 
For $t\geq\tau_\mathfrak{u}$, we can compute
\small
\begin{eqnarray*}
&&\mathbb{E}[|X^{N}_{\tau_{\mathfrak{u}}}(t+r )-X^{N}_{\tau_{\mathfrak{u}}}(t)|^2|{\cal F}_t^{
\eta}]\\
&&= \mathbb{E}\left[\left|\int_{S_{t,r}}{\bf 1}_{\{U_{\tau_{\mathfrak{u}}}(s)+\frac v{2\lambda^{-1}\theta \gamma^{\mathfrak{m}}_\theta(X^{N}_{
\tau_{\mathfrak{u}}}(s-),\overline{\eta}^{N}(s-))}<\lambda \}}\kappa 
y\Pi_{\tau_{\mathfrak{u}}}(ds,dv,dy,d\kappa )\right|^2\Bigg|{\cal F}_t^{\eta}\right]\\
&&\leq 2\mathbb{E}\left[\left|\int_{S_{t,r}}{\bf 1}_{\{v < 2 \theta \gamma^{\mathfrak{m}}_\theta(X^{N}_{
\tau}(s-),\overline{\eta}^{N}(s-))\}}{\bf 1}_{\kappa =1}
y\tilde\Pi_{\tau_{\mathfrak{u}}}(ds,dv,dy,d\kappa )\right|^2\Bigg|{\cal F}_t^{\eta}\right]\\
&&\quad +2\mathbb{E}\left[\left|\int_{t}^{t+r}\int_{\{v < 2 \theta \gamma^{\mathfrak{m}}_\theta(X^{N}_{
\tau_{\mathfrak{u}}}(s-),\overline{\eta}^{N}(s-))\}}\frac{1}{2}\left| \int_{\mathbb{R}^d} (y-X^{N}_{\tau}(s-)) q^{\mathfrak{m}}_{\theta, \varepsilon}(X^{N}_{\tau}(s-),\overline{\eta}^{N}(s-),dy) \right|
dvds \right|^2\Bigg|{\cal F}_t^{\eta}\right]\\
&&\leq 2\mathbb{E}\left[\int_{t}^{(t+r)   }\theta (1+C_G)\int_{{\mathbb{R}}^d}|y-X^{N}_{
\tau_{\mathfrak{u}}}(s)|^2q^{\mathfrak{m}}_{\varepsilon,\theta}(X^{N}_{\tau_{\mathfrak{u}}}(s),\bar{\eta}^{\varepsilon,\theta,\lambda}(s-),dy)ds\Bigg|{\cal F}_t^{\eta}\right]\\
&&\quad +2\mathbb{E}\left[\left|\int_{t}^{(t+r)    } \theta (1+C_G)\left|\int_{{\mathbb{R}}^d}
(y-X^{N}_{\tau_{\mathfrak{u}}}(s))q^{\mathfrak{m}}_{\varepsilon,\theta}(X^{N}_{\tau_{\mathfrak{u}}}(s),
\overline{\eta}^{N}(s),dy)\right|ds\right|^2\Bigg|{\cal F}_t^{\eta}\right]\\
&&\leq 2r \overline{\beta}(1+C_G)+2(r \overline{\alpha}(1+C_G))^2.\end{eqnarray*}
\normalsize

The first inequality uses the fact that $(A+B)^2 \leq 2A^2+2B^2$ as well as the definition of the transition kernel $H$. The second inequality holds because birth events occur at rate $2 \theta \gamma^{\mathfrak{m}}_{\theta}$ bounded above by $2\theta (1+C_G)$. The third inequality holds given the assumptions on the dispersal kernel.

Finally, since $\overline{\eta}_0$ has compact support, we can take $t=\tau_u$ and apply Markov inequality to get that for every $\delta>0$, there exists $N_{\delta}>0$ such that
\begin{equation}\label{eq: Compact Containment Condition for individual spatial motion}
\sup_{\varepsilon, \theta, \lambda}\sup_{T>0}\mathbb{P}\left[|X^{N}_{\tau_{\mathfrak{u}}}(\tau_{\mathfrak{u}}+T)-X^{N}_{\tau_{\mathfrak{u}}}(\tau_{\mathfrak{u}})|>N_{\delta}\right]\leq   \frac{2r \overline{\beta}(1+C_G)+2(r \overline{\alpha}(1+C_G))^2}{N_{\delta}^2}  < \delta,
\end{equation}
giving us compact containment condition. Relative compactness thus follows by Theorem 3.8.6.
of \cite{ethier/kurtz:1986}.
\end{proof}
\begin{remark}
Note that under the assumptions laid out in Theorem \ref{teo: Non-local interaction Convergence} and Theorem \ref{teo: Local Interaction Convergence}, $r \equiv 1$, so 
$$\gamma^{\mathfrak{m}}_{\varepsilon,\theta}(x, \overline{\eta})=\tilde\gamma_{\theta}(x, \varrho_{\varepsilon}*\overline{\eta})= 1+\frac{G(\varrho_{\varepsilon}*\overline{\eta})}{\theta} \leq (1+C_G)$$
for all $\theta > 1$, and 
$$q^{\mathfrak{m}}_{\varepsilon,\theta,\lambda}(x,\overline{\eta},dy)=q_{\theta}(x,dy).$$
In particular, we have the inequalities
\begin{align}
   \sup_{\varepsilon, \theta}\limsup_{x, \overline{\eta}} \theta \left| \int_{\mathbb{R}^d} (y-x) q^{\mathfrak{m}}_{ \varepsilon, \theta}(x,\overline{\eta},dy) \right| =& \sup_{\theta}\limsup_{x} \theta \left| \int_{\mathbb{R}^d} (y-x) q_{\theta}(x,dy) \right| =  0,\\
   \sup_{\varepsilon, \theta}\limsup_{x, \overline{\eta}} \theta \int_{\mathbb{R}^d} |y-x|^2 q^{\mathfrak{m}}_{ \varepsilon, \theta}(x,\overline{\eta},dy)  =& \sup_{\theta}\limsup_{x} \theta \int_{\mathbb{R}^d} |y-x|^2 q_{\theta}(x,dy) =  1,
\end{align}
as the last term can be expressed as $\theta \mathbb{E}_{x}[(B_{1/\theta}-x)^2]=1$. As a result, Lemma \ref{lem: tightness of individual spatial trajectory} holds for the setting in Theorem \ref{teo: Non-local interaction Convergence} and Theorem \ref{teo: Local Interaction Convergence}.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Tightness of Level Processes}
Proving tightness of the level process is slightly trickier as the levels of many particles will drift towards infinity in finite time. These particles however will not contribute to the metric associated with the vague topology and thus we will retain relative compactness. The main argument relies on the observation that particles with levels lower than some threshold $\overline{U}_{N, \delta}$  have regulated level increments of order $\delta$ over any small time interval of length $r$ given large enough $\lambda$. As a result, we can evaluate our level process against test functions $(g_n)_{n=1,..,N}$ with cut off smaller than $\overline{U}_{N, \delta}$.

\begin{lemma} \label{tightness of levels} For fixed $\mathfrak{u}\in \mathcal{U}$,
$\{(U^{N}_{\tau_\mathfrak{u}}(t))_{t \geq 0}, \lambda >0\}$ is relatively compact in 
$\mathcal{D}_{[0,\infty]}[0,\infty )$ where $[0,\infty]$ is equipped with the metric $\mathfrak{d}$ for the vague topology in $[0,\infty]$ (see Theorem  \ref{Vague times Euclidean is Polish}).
\end{lemma}

\begin{proof}

\textbf{Introducing a cutoff range:} It suffices to show that for any $\delta > 0$ and for any particle $\mathfrak{u} \in \mathcal{U}$, there exists small enough  $r>0$ such that $\mathbb{E}[\mathfrak{d}(U^{N}_{\tau_{\mathfrak{u}}}(t+r),U^{N}_{\tau_{\mathfrak{u}}}(t))|{\cal F}_t^{
\eta}]< \delta$. \\
For this, pick $K_{\delta} \in \mathbb{N}$ such that $\frac{1}{2^{K_{\delta}}} < \delta/2$. then we have that 
\begin{multline}
\mathfrak{d}(U^{N}_{\tau_{\mathfrak{u}}}(t+r),U^{N}_{\tau_{\mathfrak{u}}}(t))\leq  \sum_{n=1}^{K_{\delta}}\frac{1 \wedge |g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|}{2^n} +  \delta/2. 
\end{multline}
Now it suffices to prove that for small enough $r$, $|g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))| < \delta / (2K_{\delta})$.

Pick $\overline{U}_{K_{\delta}, \delta}>0$ large enough such that $\text{supp}(g_n)\subset [0,\overline{U}_{K_{\delta}, \delta}]$ for all $n=1,..,K_{\delta}$. Since we picked $g_n$ to be continuous and differentiable with compact support, by Mean Value Theorem we have that 
$$|g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|<C'_{g_1,..,g_{K_\delta}}(|U^{N}_{\tau_{\mathfrak{u}}}(t+r)-U^{N}_{\tau_{\mathfrak{u}}}(t)|\wedge \overline{U}_{K_{\delta}, \delta}), $$
uniformly over $n=1,..,K_{\delta}$ for some constant $C'_{g_1,...,g_{K_{\delta}}}$. Note that it suffices to consider $|U^{N}_{\tau_{\mathfrak{u}}}(t+r)-U^{N}_{\tau_{\mathfrak{u}}}(t)|\wedge \overline{U}_{K_{\delta}, \delta}$ because $g_n(u)=g_n(\overline{U}_{K_{\delta}, \delta})=0$ for all $u > \overline{U}_{K_{\delta}, \delta}$. We proceed to bound $|U^{N}_{\tau_{\mathfrak{u}}}(t+r)-U^{N}_{\tau_{\mathfrak{u}}}(t)|$ given that $U^{N}_{\tau_{\mathfrak{u}}}(t) < \overline{U}_{K_{\delta}, \delta}$.

\textbf{Controlling downward drift:} We first consider the case where $\tau_{\mathfrak{u}}< t$, i.e. the particle $\mathfrak{u}$ is born before time $t$. 
We have that 
\small
\begin{equation}
\begin{aligned}
U^{N}_{\tau_{\mathfrak{u}}}(t+r)-U^{N}_{\tau_{\mathfrak{u}}}(t) =  &   \int_{t}^{(t+r)  }\frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))}dV^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)\\
&+\int_{t}^{(t+r)  }\bigg(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))U^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)^2 - b_{\varepsilon, \theta, \lambda}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))U^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)\bigg)ds,
\end{aligned}
\end{equation}
\normalsize
where the first term corresponds to positive jumps and the second term corresponds to the evolution according to a quadratic differential equation. To control the downward drift of our levels from the quadratic evolution,
we neglect all positive drift and obtain
\begin{equation}
\begin{aligned}
\mathbb{E}[U^{N}_{\tau_{\mathfrak{u}}}(t+r)-U^{N}_{\tau_{\mathfrak{u}}}(t)] \geq   &   - \int_{t}^{(t+r)  } G(\varrho_{\varepsilon}*\Xi^{\varepsilon, \theta, \lambda}_s(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s))) U^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)ds\\
\geq& - rC_G\overline{U}_{K_{\delta}, \delta}.
\end{aligned}    
\end{equation}

\textbf{Controlling Upward Drift with Comparison Principle:}
On the other hand, the positive increments are due to jumps and the quadratic evolution. To control the quadratic upward drift, we apply comparison principle.

The process $(W_s)_{s \geq 0}:=(U^{N}_{\tau_{\mathfrak{u}}}(t+s)\wedge \overline{U}_{K_{\delta}, \delta})_{s \geq 0}$ satisfy the differential inequality with jumps of the form 
\begin{equation}
\begin{aligned}
 dW_s \leq& \frac{1}{2\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))}dV^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)\wedge \overline{U}_{K_{\delta}, \delta}\\
 &+\bigg(\lambda^{-1} \theta \gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))W_s^2 - b_{\varepsilon, \theta, \lambda}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s))W_s\bigg)\mathbbm{1}_{W_s \leq \overline{U}_{K_{\delta}, \delta}}ds,
\end{aligned}
\end{equation}
with initial condition $W_0=U^{N}_{\tau_{\mathfrak{u}}}(t)\leq \overline{U}_{K_{\delta},\delta}$. The first term is due to the fact that all jumps of $(U^{N}_{\tau_{\mathfrak{u}}}(t+s))_{s \geq 0}$ that lands above $\overline{U}_{K_{\delta}, \delta}$ will result in  the process $(W_s)_{s \geq 0}$ landing on $\overline{U}_{K_{\delta}, \delta}$. The indicator function in the second term is due to the process staying at $\overline{U}_{K_{\delta}, \delta}$ once the process hit the value.

Note that we have $\gamma^{\mathfrak{m}}_{\varepsilon, \theta}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s)) \leq (1+C_G),$ and $- b_{\varepsilon, \theta, \lambda}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s),\Xi^{\varepsilon, \theta, \lambda}(s)) \leq \varrho_{\varepsilon}*\Xi^{\varepsilon, \theta, \lambda}_{s}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)).$ Furthermore, recall that $V_{\tau}(t)=\sum_{k=1}^{m}v_k\mathbbm{1}_{[0, \tau_k]}  (t)  $ and all jumps are at most of size $\overline{U}_{K_{\delta}, \delta}$ for the process $(W_s)_{s \geq 0}$, By the comparison principle, for any $s \geq 0$, $W_s-W_0$ is bounded above by the increment $\widetilde{W}_s-\widetilde{W}_0$ of a process $(\widetilde{W}_s)_{s \geq 0}$ which satisfies 
\begin{equation}
\begin{aligned}
 d\widetilde{W}_s =& \overline{U}_{K_{\delta}, \delta} dN_{\tau_\mathfrak{u}}(s) +\bigg(\lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2 + \varrho_{\varepsilon}*\Xi^{\varepsilon, \theta, \lambda}_{s}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s)) \overline{U}_{K_{\delta}, \delta}\bigg)ds.
\end{aligned}
\end{equation}
Here $(N_{\tau_\mathfrak{u}}(s))_{s \geq 0}$ is the Poisson point process $N_{\tau_\mathfrak{u}}(t)=\sum_{k=1}^{m}\mathbbm{1}_{[0, \tau_k]}  (t) $ with rate $1$ and $\widetilde{W}_0 = \overline{U}_{K_{\delta}, \delta}$.

Taking expectations, we have that 
\begin{equation}
\begin{aligned}
\mathbb{E}[\widetilde{W}_{t+r}-\widetilde{W}_t] \leq &   \overline{U}_{K_{\delta}, \delta}r + \lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2r + \overline{U}_{K_{\delta}, \delta} \int_{t}^{t+r}\mathbb{E}\left[\varrho_{\varepsilon}*\Xi^{\varepsilon, \theta, \lambda}_{s}(X^{\varepsilon, \theta, \lambda}_{\tau_{\mathfrak{u}}}(s))\right]ds\\
\leq & \overline{U}_{K_{\delta}, \delta}r + \lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2r +\overline{U}_{K_{\delta}, \delta} \int_{t}^{t+r}\left(C_0
+   K' e^{C_G s}\right)e^s ds \\
= & \overline{U}_{K_{\delta}, \delta}r + \lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2r +\overline{U}_{K_{\delta}, \delta} +(C_0e^t+\frac{C_0K'}{C_G+1}e^{C_G+1})(e^{r}-1).
\end{aligned}
\end{equation}

\textbf{Controlling Increments by Birth Events:}
Now consider the scenario where $t > \tau_u$, i.e. the particle $\mathfrak{u}$ has not been born at time $t$. Denote $\mathcal{B}^{N}_{\mathfrak{u}}([t,t+r  ])$ to be the event that particle $\mathfrak{u}$ is born between $[t,t+r  ]$ with level smaller than $U_{K_{\delta}, \delta}$. In this case,
\begin{multline}
 |g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|\\
 =g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))\times\mathbbm{1}_{\mathcal{B}^{N}_{\mathfrak{u}}([t,t+r  ])}\\
 < C_{g_1,...,g_n}\times \mathbbm{1}_{\mathcal{B}^{N}_{\mathfrak{u}}([t,t+r  ])},   
\end{multline}
for some uniform bound $C_{g_1,...,g_n}$ over $\{||g_n||_{\infty}: n =1,...,N \}$. It suffices therefore to show that the probability for a particle $\mathfrak{u}$ to be born or gives birth in some time interval of length less than or equal to $r$ can be arbitrarily small given small enough $r$. Let $\mathcal{N}^{N}_{\mathfrak{u}}([t,t+r  ])$ to be the number of particles born between $[t,t+r]$ with level smaller than $U_{K_{\delta}, \delta}$. Then 
\begin{equation}
\begin{aligned}
\mathbb{P}[\mathcal{B}^{N}_{\mathfrak{u}}([t,t+r  ])]  \leq&  \mathbb{P}[\mathcal{N}^{N}_{\mathfrak{u}}([t,t+r  ]) \geq 1]\\
\leq & \mathbb{E}[\mathcal{N}^{N}_{\mathfrak{u}}([t,t+r  ]) ].
\end{aligned}
\end{equation}
Recall that we have bounds over the total mass of the particle systems, so at time $t$, the expected number of particles alive in the $N$-th stage of scaling is bounded above $\lambda_NC_0e^{C_Gt}$ (with $\lambda_N=N$). The particles have levels that are independently and uniformly distributed between $[0, \lambda_N]$. Therefore, the expected number of particles with levels between $[0,U_{K_{\delta}, \delta}]$ is $U_{K_{\delta}, \delta}C_0e^{C_Gt}$. The number of births within an interval of length $r$ is a sum of Poisson random variables, and so we have 
$$\mathbb{E}[\mathcal{N}^{N}_{\mathfrak{u}}([t,t+r  ]) ]=U_{K_{\delta}, \delta}C_0e^{C_Gt}r.$$

\textbf{Conclusion:} Combining all of the above results, we have that for any $\delta > 0$,
\begin{equation}
\begin{aligned}
\mathbb{E}[\mathfrak{d}(U^{N}_{\tau_{\mathfrak{u}}}(t+r),U^{N}_{\tau_{\mathfrak{u}}}(t))] \leq & \mathbb{E}\left[\sum_{n=1}^{K_{\delta}}\frac{1 \wedge |g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|}{2^n}\right] +  \delta/2\\
\leq &\mathbb{E}\left[\sum_{n=1}^{K_{\delta}}\frac{1 \wedge |g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|}{2^n}: \tau_{\mathfrak{u}} \leq t \right]\\
& + \mathbb{E}\left[\sum_{n=1}^{K_{\delta}}\frac{1 \wedge |g_n(U^{N}_{\tau_{\mathfrak{u}}}(t+r))-g_n(U^{N}_{\tau_{\mathfrak{u}}}(t))|}{2^n}: \tau_{\mathfrak{u}} \geq t \right] + \delta/2\\
\leq & C'_{g_1,...,g_n}\bigg(\overline{U}_{K_{\delta}, \delta}r + \lambda^{-1} \theta (1+C_G)\overline{U}_{K_{\delta}, \delta}^2r\\
& \qquad \qquad  +\overline{U}_{K_{\delta}, \delta} +(C_0e^t+\frac{C_0K'}{C_G+1}e^{C_G+1})(e^{r}-1)\bigg)\\
& + C'_{g_1,...,g_n}U_{K_{\delta}, \delta}C_0e^{C_Gt}r+\delta/2\\
< & \delta 
\end{aligned}    
\end{equation}
for small enough $r>0$. In particular, this choice of $r$ is independent of $\varepsilon, \theta, \lambda$. Therefore we have proved tightness of our level processes by \cite{EK} Theorem 3.8.6.
\end{proof}
\subsubsection{Convergence in $\mathcal{D}_{[0,\infty)}\left(\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)\right)$ to $(\xi^{ \infty}_t)_{t \geq 0}$, where $\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)$}
Now that we have proven tightness for individual level and spatial trajectories, by Corollary \ref{cor: convergence in p implies convergence in p-infty}, Lemma \ref{lem: Countable Implies Vague} and Theorem \ref{teo: Theorem A12 Kurtz Rodrigues generalised}, we have proved that the particle system $(\xi^{\varepsilon_N, \theta_N,\lambda_N}_t)_{t \geq 0}$ converges in $\mathcal{D}_{[0,\infty)}\left(\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)\right)$ to $(\xi^{ \infty}_t)_{t \geq 0}$, where $\mathcal{N}_f(\mathbb{R}^d \times [0, \infty)$ is equipped with the $\mathfrak{p}^{wv}$-topology. Furthermore, its spatial projection $(\overline{\eta}^{\varepsilon_N, \theta_N,\lambda_N}_t)_{t \geq 0}$ converges to $(\overline{\eta}^{\infty}_t)_{t \geq 0}$ in $\mathcal{D}_{[0,\infty)}\left(\mathcal{M}_f(\mathbb{R}^d \right)$, where $\mathcal{M}_f(\mathbb{R}^d)$ is equipped with the weak topology.

In the next section, we will show how we identify the limit process.

@@

\end{proof}
\section{Topological Results on Lookdown Representations}
\label{sec: Topologies on Lookdown}

\subsection{Euclidean-Vague Topology on $\mathbb{R}^d \times [0,\infty]$}\label{sec: Convergence in Product Topology}
We first define a topology on $\mathbb{R}^d \times [0,\infty]$ which is Euclidean on $\mathbb{R}^d$ and vague in $[0,\infty]$.
\begin{definition}
We define the topology $\mathfrak{p}$ on $\mathbb{R}^d \times [0,\infty]:$
we say $(x_n,u_n) \to (x,u)$ in topology $\mathfrak{p}$ if 
\begin{enumerate}
    \item $|x_n-x| \to 0$ in $\mathbb{R}^d$.
    \item  For all $g \in C_{c}([0,\infty])$, the space of continuous functions with compact support on $[0,\infty]$, $g(u_n) \to g(u).$ Since this is the vague convergence for $(\delta_{u_n})_{n \in \mathbb{N}}$ we will abuse a bit the notation and denote this by the symbol $u_n \xrightarrow{vague} u$. 
\end{enumerate}
\end{definition}

In other words, our topology is Euclidean in space $\mathbb{R}^d$ and vague in levels in $[0,\infty]$.
\begin{lemma}\label{Vague times Euclidean is Polish}
The space $\mathbb{R}^d \times [0,\infty]$ under topology $\mathfrak{p}$ is Polish.
\end{lemma}
\begin{proof}
The space $C_c([0,\infty])$ is dense, so we pick a countable dense subset $S:=\{h_n: n \in \mathbb{N}\} \subset C^{1}_c([0,\infty])$ and define the metric $\mathfrak{d}$ such that $\mathfrak{d}(u,v)=\sum_{n=1}^{\infty}\frac{1 \wedge |h_n(u)-h_n(v)|}{2^n}$.

Assume that $u_n \xrightarrow{vague} u$. Pick arbitrary $\delta>0$ and take $N$ large enough such that $\frac{1}{2^N}<\delta/2$. Furthermore, pick $n$ large enough such that $\inf_{i=1,2,...,N}|h_i(u_n)-h_i(u)|<\delta/2$. From this we immediately have that $\mathfrak{d}(u_n,u)<\delta$. Thus $\mathfrak{d}(u_n,u) \to 0$.

Conversely assume that $\mathfrak{d}(u_n,u) \to 0$. For any $h \in \mathcal{C}^{1}_c([0,\infty])$ and for any $\delta>0$, pick $g_N$ such that $||h-h_N||_{\infty}<\delta /3$ and $n$ large enough such that $\mathfrak{d}(u_n,u)< \frac{\delta}{3 \times 2^N}$. Then $|h(u)-h(u_n)|< |h(u)-h_N(u)|+|h_N(u)-h_N(u_n)|+|h_N(u_n)-h(u_n)|<\delta$, and so $h(u_n) \to h(u)$.

Finally, one can easily check that $\mathbb{Q}$ is a countable dense set in $[0,\infty]$ equipped with the metric $\mathfrak{d}$.
Defining the metric $d_{\mathfrak{p}}$
by
$$d_{\mathfrak{p}}((x_1,u_1),(x_2,u_2))=||x_1-x_2||+\mathfrak{d}(u_1,u_2),$$
we can show easily that
convergence in $d_{\mathfrak{p}}$
is equivalent to convergence in 
$\mathfrak{p}$ topology.
\end{proof}

\subsection{Weak-Vague Topology on Measures}\label{sec: Empirical Measure Topology}

We now characterise the lookdown representation
of our particle system
as a measure on 
$(\mathbb{R}^d \times [0, \infty], \mathfrak{p})$.
We endow the vague topology
on these measures for
convergence of lookdown representations.
We refer to Theorem A.23 and Theorem A.24 in \cite{kallenberg1997foundations}.

First of all,
as $(\mathbb{R}^d \times [0, \infty], \mathfrak{p})$
is Polish,
the family of $C^{+}_K$ of continuous functions
$$f: \mathbb{R^d} \times [0, \infty] \to \mathbb{R}^{+}$$
with compact support
is separable in the uniform metric. 
The sets $K_n =[-n, n]^d \times [0,n]$ clearly forms a sequence of compact sets and $K_n \uparrow \mathbb{R^d} \times [0, \infty]$.

We denote $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$ as the class of measures on $\mathbb{R^d} \times [0, \infty]$ that are 
locally finite (i.e. bounded on bounded intervals),
and write $\pi_B, \pi_f$ 
for the mappings 
$\mu \to \mu B$, $\mu \to \mu f := \int f d\mu$,
respectively,
on $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$.

The \textit{vague topology} in $\mathcal{M}(\mathbb{R^d} \times [0, \infty)$ is generated by the maps $\pi_f, f \in C^{+}_K$, and 
we write the cague convergence of $\mu_n$ toward $\mu$
as $\mu_n \xrightarrow{v} \mu$.

Taking $S= \mathbb{R^d} \times [0, \infty]$
in Theorem A.23
in \cite{kallenberg1997foundations},
we have
\begin{theorem}[vague topology]
\label{teo: Kallenberg vague results}

The following holds:
\begin{enumerate}
    \item $\mathcal{M}(\mathbb{R^d} \times [0, \infty])$ is a Polish space in the vague topology
    \item A set $A \subset \mathcal{M}(\mathbb{R^d} \times [0, \infty])$ is vaguely relatively compact iff 
    $\sup_{\mu \in A} \mu f < \infty$ for all $f \in C^{+}_K$
    \item if $\mu_n \xrightarrow{v} \mu$ and a set $B$ is finite with $\mu \partial B = 0$, then $\mu_n B \to \mu B$.
\end{enumerate}

\end{theorem}
